Weakly Nonlinear MRI: Notes

### 2014-10-20 notes/mri_notes.tex
all hmri terms... where to go from here?

\beq
\xi^2 B_0^2 \frac{x_1^2}{x^3} \hat{x} \, - \,  \xi B_0 \frac{x_1}{x^2} B_{1x} \hat{y} \, + \, \xi B_0 \frac{x_1}{x^2} B_{1y} \hat{x} \, - \, \partial_z B_{1y} \xi B_0 \frac{x_1}{x} \hat{z} \, - \, \partial_x B_{1y} \xi B_0 \frac{x_1}{x} \hat{x}
\eeq

@@

\beq
\partial_t \mathbf{B} = \left( \left( \mathbf{B_0} \hat{z} + \xi B_0 \frac{x_1}{x} \hat{y} + \mathbf{B_1} \right) \cdot \nabla \right) \left(-q \Omega_0 x \hat{y} + \mathbf{u_1}\right) = \xi B_0 \frac{x_1}{x} \partial_y \mathbf{u_1}
\eeq

@@

\beq
\xi B_0 u_{1x} \frac{x_1}{x^2} \hat{y}
\eeq

>>>>

\beq
\label{momeq_added}
\xi^2 B_0^2 \frac{x_1^2}{x^3} \hat{x} \, - \,  \xi B_0 \frac{x_1}{x^2} B_{1x} \hat{y} \, + \, \xi B_0 \frac{x_1}{x^2} B_{1y} \hat{x} \, - \, \partial_z B_{1y} \xi B_0 \frac{x_1}{x} \hat{z} \, - \, \partial_x B_{1y} \xi B_0 \frac{x_1}{x} \hat{x}
\eeq

@@

\beq
\left( \left( \mathbf{B_0} \hat{z} + \xi B_0 \frac{x_1}{x} \hat{y} + \mathbf{B_1} \right) \cdot \nabla \right) \left(-q \Omega_0 x \hat{y} + \mathbf{u_1}\right) = \xi B_0 \frac{x_1}{x} \partial_y \mathbf{u_1}
\eeq

@@

\beq
-\left( \left( -q \Omega_0 x \hat{y} + \mathbf{u_1}\right) \cdot \nabla\right) \left( B_0 \hat{z} + \xi B_0 \frac{x_1}{x} \hat{y} + \mathbf{B_1}\right)   \, = \, \xi B_0 u_{1x} \frac{x_1}{x^2} \hat{y}
\eeq

And the third term on the righthandside becomes

\beq
\frac{1}{\reym} \xi B_0 \left( \frac{2 x_1}{x^3}\right) \hat{y}
\eeq

So that all told, the induction equation gains the terms:

\beq
\xi B_0 \frac{x_1}{x} \partial_y \mathbf{u_1} \, + \, \xi B_0 u_{1x} \frac{x_1}{x^2} \hat{y} \, + \, \frac{1}{\reym} \xi B_0 \left( \frac{2 x_1}{x^3}\right) \hat{y}
\eeq

Because the $\partial_y$ terms go to zero, the induction equation only picks up terms in its $y$ component (the first term above goes to zero). Rewritten to use the stream function, these terms are:

\beq
\label{induc_eq_added}
\xi B_0 \frac{x_1}{x^2} \partial_z \Psi \hat{y} + \frac{1}{\reym} \xi B_0 \frac{2 x_1}{x^3} \hat{y}
\eeq

We can now inspect Equation \ref{momeq_added} and see that the $\hat{y}$ component of the momentum equation will pick up a term analogous to the the first term of Equation \ref{induc_eq_added} -- a tantalizing $\partial_z$ term, which has the ability to lend a $\partial_Z$ term in the $\mathcal{O}\left(\epsilon^2\right)$ equation! But Equation \ref{momeq_added} can no longer be written in terms of flux/stream functions, because contributions to the $\hat{x}$ and $\hat{z}$ components are uneven. Should I rewrite all the equations in terms of primitive variables to proceed?
